Union and intersection contracts are hard, actually

### 2021-09-15 paper.tex

>>>>

\subsection{Context sensitive contracts}

The work by Dimoulas et al.~\cite{dimoulasESOP,dimoulasPOPL} presents
a complete study on systems that may execute (and potentially invalidate)
contracts inside other contracts, in particular through the study
of dependent function contracts.
Their ideas have the potential to help solve the problems outlined
on Sections \ref{sec:flat-and-inter} and \ref{sec:keil-thiemann},
however, we consider it's not clear how to leverage their techniques
for intersections.

As a first obstacle, it's worth noting that their system is intended
to get stuck upon the checking of a contract in a context that shouldn't
be checked in, while to keep the semantics of unions and intersections
valid, we'd expect for that check to get skipped, and for execution
to continue.

% > Also worth noting is that Dimoulas's work deals extensively with these kinds
% > of contracts and there is no mention of it in this paper. His POPL 2011 and
% > ESOP 2012 papers are relevant to such contracts.

% Regarding Dimoulas's papers, their work presents a solution
% for contracts that may, arbitrarily, break other contracts in their
% evaluation. Although this looks related to this problem with
% intersection and user-defined contracts, it is not clear how to
% leverage Dimoulas's techniques for intersection in practice.

% It's worth noting, for instance, that Dimoulas's systems behave by getting stuck
% in the case an undesired event happens (a contract fails because of external,
% semantically unrelated, values flow in). With unions and intersections as
% developed by Keil and Thiemann, the expected outcome is rather to not execute a
% contract under the wrong context.
